A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-01-28 paper.tex
Added syntcomp results to evaluation and wrote some analysis

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[y=0.04cm, x=0.15cm]
        %axis
        \draw (0,0) -- coordinate (x axis mid) (60,0);
            \draw (0,0) -- coordinate (y axis mid) (0,150);
            %ticks
            \foreach \x in {0,10,...,60}
                \draw (\x,1pt) -- (\x,-3pt)
                node[anchor=north] {\x};
            \foreach \y in {0,25,...,150}
                \draw (1pt,\y) -- (-3pt,\y) 
                    node[anchor=east] {\y}; 
        %labels      
        \node[below=0.8cm] at (x axis mid) {Time (min)};
        \node[rotate=90, above left=1cm and 0.7cm] at (y axis mid) {Instances solved};

@@

The implementation of our algorithm uses \textsc{Glucose}~\cite{audemard2014}
for SAT solving and \textsc{Periplo}~\cite{rollini2013} for interpolant
generation. We compared our implementation to two solvers that competed in the
sequential realisability track of SYNTCOMP'15.  \textsc{Simple BDD
Solver}~\cite{walker2014} because it had the best results in the track, and
\textsc{Demiurge}~\cite{bloem2014} because it was the only SAT-based tool to
compete. The benchmarks were run on a cluster of Intel Quad Core Xeon E5405
CPUs with 16GB of memory. Each solver was allowed exclusive access to a node
for one hour to solve an instance.

Our implementation was able to solver 103 out of the 250 specification in the
alloted time, including 10 instances that were unable to be solved by any other
solver including all other solvers in SYNTCOMP'15. \textsc{Simple BDD Solver}
and \textsc{Demiurge} were able to solve X and Y respectively. Something about
us vs BDDs and us vs demiurge with numbers of specs.

Four of the previously unsolved instances are device driver instances and
another five are toy examples. This supports the hypothesis that different game
solving methodologies perform better on certain classes of specifications.

>>>>

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[y=0.04cm, x=0.15cm]
        %axis
        \draw (0,0) -- coordinate (x axis mid) (60,0);
            \draw (0,0) -- coordinate (y axis mid) (0,150);
            %ticks
            \foreach \x in {0,10,...,60}
                \draw (\x,1pt) -- (\x,-3pt)
                node[anchor=north] {\x};
            \foreach \y in {0,25,...,150}
                \draw (1pt,\y) -- (-3pt,\y) 
                    node[anchor=east] {\y}; 
        %labels      
        \node[below=0.8cm] at (x axis mid) {Time (minutes)};
        \node[rotate=90, above left=1cm and 0.7cm] at (y axis mid) {Instances solved};

@@

The implementation of our algorithm uses \textsc{Glucose}~\cite{audemard2014}
for SAT solving and \textsc{Periplo}~\cite{rollini2013} for interpolant
generation. We compared our implementation to
\textsc{Demiurge}~\cite{bloem2014}, the only SAT-based solver to compete in the
sequential realisability track of SYNTCOMP'15. The benchmarks were run on a
cluster of Intel Quad Core Xeon E5405 CPUs with 16GB of memory.  Each solver
was allowed exclusive access to a node for one hour to solve an instance.

Our implementation was able to solver 103 out of the 250 specification in the
alloted time, including 12 instances that were unable to be solved by any other
solver in SYNTCOMP'15. \textsc{Demiurge} was able to solve 136 specifications.
77 of those instances were also solved by our implementation, so
\textsc{Demiurge} solved 59 instances that our solver did not. However, our
method was able to solve 26 specifications not solved by \textsc{Demiurge}.

For reference, the results of the synthesis competition are shown in
Figure~\ref{fig:syntcomp}. The competition ran on better hardware with a longer
time period, which explains why \textsc{Demiurge} performed better.

\begin{figure}
    \centering
    \setlength{\tabcolsep}{8pt}
    \begin{tabular}{l | r | r }
        \textbf{Solver} & \textbf{Solved} & \textbf{Unique} \\
        \hline
        Simple BDD Solver (2) & 195 & 10 \\
        AbsSynthe (seq2) & 187 & 2 \\
        Simple BDD Solver (1) & 185 & \\
        AbsSynthe (seq3) & 179 & \\
        Realizer (sequential) & 179 & \\
        AbsSynthe (seq1) & 173 & 1 \\
        Demiurge (D1real) & 139 & 5 \\
        Aisy & 98 & \\
        \hline
        Unbounded Synthesis & 103 & 12 \\
    \end{tabular}
    \caption{Synthesis Competition 2015 Results}
    \label{fig:syntcomp}
\end{figure}

Five of the instances unique to our solver are device driver instances and
another five are from the \texttt{stay} family, which are classified as toy
instances.  Out of the 26 instances that \textsc{Demiurge} could not solve,
there were only 6 different benchmark classes. This supports the hypothesis
that different game solving methodologies perform better on certain classes of
specifications.

Whilst our solver is unable to solve as many instances as other tools yet, it
was able to solve more unique instances than any solver in the competition.
This shows that the method has potential. In the parallel track,
\textsc{Demiurge} competes with a suite of 3 separate but communicating
solvers. The solvers relay unsafe states to one another, which is compatible
with the set $B^M$ in our solver. It remains future work to explore the
possibility of combining these solvers.
